Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-27 article.tex
some changes : figs + tab

\author{\Name{Antonio Sutera,
    Arnaud Joly,
        Vincent François-Lavet,\\
        Aaron Qiu,
        Gilles Louppe,
        Damien Ernst,
        Pierre Geurts}
  \Email{a.sutera@ulg.ac.be}\\
  \addr Department of EE and CS \& GIGA-R, University of Li\`ege, Belgium}

%\jmlrauthors{A. Sutera et al}
%\shortauthor{A. Sutera et al.}

@@

\begin{figure}
\centering
\subfigure[Raw signal]{\includegraphics[width=0.3\textwidth]{images/original_curve.pdf} \label{fig:original_curve}}
\subfigure[Low-pass filter $f_1$]{\includegraphics[width=0.3\textwidth]{images/filter_curve.pdf} \label{fig:lp_curve}}
\subfigure[High-pass filter $g$]{\includegraphics[width=0.3\textwidth]{images/diff_curve.pdf} \label{fig:hp_curve}}\\
\subfigure[Hard-threshold filter $h$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}
\subfigure[Global regularization $w$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:weight_curve}}
\caption{Signal processing process for extracting peaks from the raw fluorescence data.
         \textcolor{red}{AJ: The bottom axe is hidden on some figures.}}
\label{fig:filtered-signal}
\end{figure}

@@

\begin{table}[t]\label{tab:comparison}
%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
\centering
\small
\begin{tabular}{| l | c c c c | c c c c |}
\hline
& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
\textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
\hline
\hline
No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
$ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
$ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
+ PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
Averaging           					& 0.938 & 0.936 & 0.936 & 0.932 & 0.391 & 0.389 & 0.385 & 0.374\\
Full method           					& 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
\hline
PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
GENIE3 & & & & & & & & \\
\hline
\end{tabular}
\caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
\end{table}

@@

@@

\vspace{5cm}

@@

\begin{table}
\small
\centering
\begin{tabular}{@{}l *{8}{c}@{}}
  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
\hline \hline
Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
\hline \hline
% Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
Pearson correlation    & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
GENIE3 (depth = 1)     & 0.878 & 0.877 & 0.873 & 0.873 & 0.184 & 0.173 & 0.182& 0.172\\
GENIE3 (depth = 2)     & 0.889 & 0.888 & 0.883 & 0.884* & 0.217 & 0.210 & 0.220 & 0.199* \\
GENIE3 (depth = 3)     & 0.892 & 0.891* & 0.887 & 0.887 & 0.232 & 0.226* & 0.237 & 0.215\\
GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
Partial correlation (avg.) & 0.938 & 0.936 & 0.936 & 0.932& 0.391 & 0.389 & 0.385 & 0.374\\
% Our approach simple + dir & 0.939 & 0.936 & 0.937 & 0.933& 0.392 & 0.390 & 0.386 & 0.375\\
Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
Our approach (opt. \& avg.)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
% Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
\end{tabular}
\caption{TODO (* means not 10000 trees but more than 9500, to be solved.) }
\label{tab:tab1}
\end{table}

>>>>

  \author{\Name{Antonio Sutera} ,
   \Name{Arnaud Joly},
   \Name{Vincent François-Lavet}, \Email{a.sutera@ulg.ac.be}\\
   \Name{Aaron Qiu},
   \Name{Gilles Louppe},
   \Name{Damien Ernst}\and\Name{Pierre Geurts}
    \\
   \addr Department of EE and CS \& GIGA-R, University of Li\`ege, Belgium}

% \author{\Name{Antonio Sutera,
%     Arnaud Joly,
%         Vincent François-Lavet,\\
%         Aaron Qiu,
%         Gilles Louppe,
%         Damien Ernst,
%         Pierre Geurts}
%   \Email{a.sutera@ulg.ac.be}\\
%   \addr Department of EE and CS \& GIGA-R, University of Li\`ege, Belgium}

\jmlrauthors{A. Sutera et al}
% \shortauthor{A. Sutera et al.}

@@

\begin{figure}
\centering
\subfigure[Raw signal]{\includegraphics[width=0.3\textwidth]{images/original_curve.pdf} \label{fig:original_curve}}
\subfigure[Low-pass filter $f_1$]{\includegraphics[width=0.3\textwidth]{images/filter_curve.pdf} \label{fig:lp_curve}}
\subfigure[High-pass filter $g$]{\includegraphics[width=0.3\textwidth]{images/diff_curve.pdf} \label{fig:hp_curve}}\\
\subfigure[Hard-threshold filter $h$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}
\subfigure[Global regularization $w$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:weight_curve}}
\caption{Signal processing process for extracting peaks from the raw fluorescence data.}
\label{fig:filtered-signal}
\end{figure}

@@

\begin{table}[t]\label{tab:comparison}
%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
\centering
\small
\begin{tabular}{| l | c c c c | c c c c |}
\hline
& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
\textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
\hline
\hline
No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
$ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
$ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
+ PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
Full method           					& 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
\hline
PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
GENIE3 & & & & & & & & \\
\hline
\end{tabular}
\caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
\end{table}

@@

\begin{table}[t]\label{tab:comparison}
%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
\centering
\small
\begin{tabular}{| l | c c c c c c | c c c c c c|}
\hline
& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
\textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{normal-3-highrate} & \textit{normal-4-lownoise} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{normal-3-highrate} & \textit{normal-4-lownoise}\\
\hline
\hline
% No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
% $ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
% $ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
% + PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
% Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
% Full method           					& 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
% \hline
% PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
% GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
% GENIE3 & & & & & & & & \\
% \hline
\end{tabular}
\caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
\end{table}

@@

%\vspace{5cm}

@@

\begin{table}
\small
\centering
\begin{tabular}{@{}l *{8}{c}@{}}
  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
\hline \hline
Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
\hline \hline
% Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
Pearson correlation    & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
GENIE3 (depth = 1)     & 0.878 & 0.877 & 0.873 & 0.873 & 0.184 & 0.173 & 0.182& 0.172\\
GENIE3 (depth = 2)     & 0.889 & 0.888 & 0.883 & 0.884* & 0.217 & 0.210 & 0.220 & 0.199* \\
GENIE3 (depth = 3)     & 0.892 & 0.891* & 0.887 & 0.887 & 0.232 & 0.226* & 0.237 & 0.215\\
GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
Partial correlation (avg. 2) & 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375  \\
Partial correlation (avg. 4) & 0.938 & 0.936 & 0.936 & 0.932& 0.391 & 0.389 & 0.385 & 0.374\\
% Our approach simple + dir & 0.939 & 0.936 & 0.937 & 0.933& 0.392 & 0.390 & 0.386 & 0.375\\
Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
Our approach (opt. \& avg. 4)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
% Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
\end{tabular}
\caption{TODO (* means not 10000 trees but more than 9500, to be solved.) }
\label{tab:tab1}
\end{table}
